---
title: "Reproducible science workshop"
description: "A one-day workshop with `R` and `RStudio`"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```


Who: [Olivier Gimenez](https://oliviergimenez.github.io/)  
When: March 18, 2021  
Where: Zoom  
<!-- Syllabus: [click here](syllabus.html)   -->
<!-- Upcoming lectures and assignments: [click here](schedule.html)   -->

# Timeline

* Motivations (20 minutes)
* Manipulating data in the `tidyverse` (80 minutes)
* Visualising data in the `tidyverse` (80 minutes)
* Lunch break (90 minutes)
* Writing dynamic and reproducible documents with `R Markdown` (60 minutes)
* Versioning with `Git` and `GitHub` in `RStudio` (60 minutes)
* Take-home messages (30 minutes)

# Requirements

* You will need a GitHub account, you can easily set up a free account [here](https://github.com/).

* To run the workshop materials on your machine, you will need:

    - The latest version of `R`, [download here](https://cloud.r-project.org/).
    - The latest version of `RStudio`, [download here](https://rstudio.com/products/rstudio/download/#download).
    - The following `R` packages: `tidyverse`, `sf`, `emo`, `janitor`, `palmerpenguins`, `usethis` and `lubridate.` You can install them all at once by running the following code in the `R` command line:

```{r eval = FALSE, echo = TRUE}
install.packages(c("tidyverse", "sf", "emo", "janitor", "palmerpenguins", "usethis", "lubridate"))
```


## Corrections {.appendix}

If you see mistakes or want to suggest changes, please [create an issue](https://github.com/oliviergimenez/reproducible-science-workshop/issues) on the source repository.

## Reuse {.appendix}

Text and figures are licensed under Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/). Any computer code (R, HTML, CSS, etc.) in slides and worksheets, including in slide and worksheet sources, is also licensed under [MIT](https://github.com/oliviergimenez/reproducible-science-workshop/blob/master/LICENSE.md). 
