---
title: Writing a report with R Markdown
subtitle: Practical
output:
  xaringan::moon_reader:
    css: ["assets/css/xaringan-themer.css", "assets/css/custom.css"]
    lib_dir: "assets/libs"
    seal: true
    yolo: false
    self_contained: false
    nature:
      ratio: "4:3"
      titleSlideClass: ["right", "middle"]
      highlightStyle: 'zenburn'
      highlightLines: false
      countIncrementalSlides: false
      slideNumberFormat: "%current% / %total%"
      beforeInit: "../../assets/libs/macros.js"
---

## Context

Let's apply what we have learnt in the course on [Writing dynamic and reproducible documents - An introduction to R Markdown](https://oliviergimenez.github.io/intro_rmarkdown/#1). 

We will use the awesome `palmerpenguins` dataset `r emo::ji("penguin")`, an alternative to Fisher's `iris` dataset, to explore and visualize data.

These data have been collected and shared by [Dr. Kristen Gorman](https://www.uaf.edu/cfos/people/faculty/detail/kristen-gorman.php) and [Palmer Station, Antarctica LTER](https://pal.lternet.edu/). 

The package was built by Drs Allison Horst and Alison Hill, check out the [official website](https://allisonhorst.github.io/palmerpenguins/). 

The package `palmerpenguins` has two datasets. 

```{r showdata}
library(palmerpenguins)
data(package = 'palmerpenguins')
``` 

---

The dataset `penguins` is a simplified version of the raw data; see `?penguins` for more info: 

```{r example-penguins}
head(penguins)
```

---

The other dataset `penguins_raw` has the raw data; see `?penguins_raw` for more info: 

```{r example-penguins-raw}
head(penguins_raw)
```


For this exercise, we're gonna use the `penguins` dataset. 


---

## Questions

**1)** Install the package `palmerpenguins`.

**2)** Create a new R Markdown document, name it and save it. Delete everything after line 12. Add a new section title, simple text and text in bold font. Compile ("Knit").  

**3)** Add a chunk in which you load the `palmerpenguins`. The corresponding line of code should be hidden in the output. Load also the `tidyverse` suite of packages. Modify the defaults to suppress all messages. 

**4)** Add another chunk in which you build a table with the 10 first rows of the dataset.

**5)** In a new section, display how many individuals, penguins species and islands we have in the dataset. This info should appear directly in the text, you might want to use inline code `r emo::ji("smile")`. Calculate the mean of the (numeric) traits measured on the penguins.

---

**6)** In another section, entitled 'Graphical exploration', build a figure with 3 superimposed histograms, each one corresponding to the body mass of a species.  

**7)** Instal package `citr`; if everything goes well, you should see it in the pulldown menu `Addins` `r emo::ji("muscle")`. Pick a recent publication from the researcher who shared the data, Dr Kristen Gorman. Import this publication in your favorite references manager (we use Zotero, no hard feeling), and create a bibtex reference that you will add to to the file `mabiblio.bib`. Add `bibliography: mabiblio.bib` at the beginning of your R Markdown document (YAML). Cite the reference iin the text using `Insert citations` in the pull-down menu `Addins`. Compile. 

**8)** Change the default citation format (Chicago style) into the The American Naturalist format. It can be found here  <https://www.zotero.org/styles>. To do soo, add `csl: the-american-naturalist.csl` in the YAML.

**9)** Build your report in html, pdf and docx format. `r emo::ji("tada")`
